Efficient ancestry and mutation simulation with msprime 1.0

### 2021-11-19 paper.tex
Tweaks

\begin{table}
\begin{tabular}{lp{12cm}}
Interface
& Separation of ancestry and mutation simulations. Integration
with forward simulators such as \SLiM\ and \fwdpy.
Rich suite of analytical and visualisation methods via \tskit\ library. \\
\midrule

Ancestry
& SMC, SMC', Beta- and Dirac-coalescent, discrete time Wright-Fisher,
  and selective sweep models. Instantaneous bottlenecks.
  Discrete or continuous coordinates, arbitary ploidy,
  gene conversion.
  Recording full ARG, full migration history, census
  events.  More efficient for large numbers of populations.\\

@@

Mutations
& JC69, HKY, F84, GTR, BLOSUM62, PAM, infinite alleles, SLiM and
general matrix mutation models.
Varying rates along the genome, recurrent/back mutations,
discrete or continuous coordinates, overlaying multiple layers
of mutations, exact times associated with mutations,
restricted time interval.\\

\end{tabular}
\caption{Major features of \msprime\ 1.0 new since version
0.3.0~\citep{kelleher2016efficient}.}
\end{table}

>>>>

\begin{table}
{ % begin box to localize effect of arraystretch change
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{lp{12cm}}
Interface
& Separation of ancestry and mutation simulations. Integration
with forward simulators such as \SLiM\ and \fwdpy.
Ability to store arbitrary metadata along with simulation
results, and automatic recording of provenance information
for reproducibility.
Rich suite of analytical and visualisation methods via \tskit\ library. \\

Ancestry
& SMC, SMC', Beta- and Dirac-coalescent, discrete time Wright-Fisher,
  and selective sweep models. Instantaneous bottlenecks.
  Discrete or continuous genomic coordinates, arbitary ploidy,
  gene conversion.
  Recording full ARG, full migration history, census
  events.  More efficient for large numbers of populations.\\

@@

Mutations
& JC69, HKY, F84, GTR, BLOSUM62, PAM, infinite alleles, SLiM and
general matrix mutation models.
Varying rates along the genome, recurrent/back mutations,
discrete or continuous genomic coordinates, overlaying multiple layers
of mutations, exact times associated with mutations,
restricted time interval.\\

\end{tabular}
}
\caption{Major features of \msprime\ 1.0 new since version
0.3.0~\citep{kelleher2016efficient}.}
\end{table}
